Manuscript_Github_Pchabaudi_pir

### 2022-07-25 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_pirAnalysis.Rmd
Phaseogram heatmap now has the max/min tpm annotation working again

library('readr')
library('dplyr')
library('ggplot2')
library("RColorBrewer")
library('data.table')
library('tibble')
library('stringr')
library('kableExtra')
library('viridis')
library('reshape2')
library('ComplexHeatmap')
library('circlize') # for circular plots and colour
library("factoextra")

@@

phaseogram_time_order <- lapply(names(phaseogram_row_order), 
                                function(list_element){
                                  transmission_list <- getElement(phaseogram_row_order,
                                                                  list_element)
                                  order_by_time <- transmission_list$zscore_order %>% 
                                    mutate(stage = times_stages_table$time[match(stage,
                                                                                 times_stages_table$r_stage_diff_count)]) %>% 
                                    arrange(stage)
                                  return(list(zscore_order = order_by_time))
                                }
)
names(phaseogram_time_order) <- names(phaseogram_row_order)

@@

    filter_genes_vector <- filter_genes_vector[!filter_genes_vector %in% remove_genes]

@@

                       if(tpm_mat){
                         #Get max/min TPM scores for the side annotation heatmap                       
                         tpm_mat <- list_element$tpm[match(rownames(heatmap_data),
                                                           list_element$tpm$Geneid),] %>%
                           select(-Geneid) %>% 
                           as.matrix %>% 
                           log1p

                         tpm_min <- rowMins(tpm_mat)
                         tpm_max <- rowMaxs(tpm_mat)

@@

                         tpm_ha <- rowAnnotation(
                           min.max = anno_simple(cbind(tpm_min, 
                                                       tpm_max), 
                                                 col = tpm_col_fun,
                                                 gp = gpar(col = 'black',
                                                           lwd = 0.1),
                                                 border = TRUE,
                                                 simple_anno_size = unit(0.2, "cm")),
                           show_annotation_name = FALSE)
                       }

                       #Draw the left annotation is needed, only for the first element.

@@

  if(tpm_mat){
    #Draw the legend
    tpm_lgd <- Legend(
      title = "Min/Max log(TPM + 1)", 
      col = tpm_col_fun, 
      at = tpm_breaks, 
      labels = tpm_breaks,
      title_gp = gpar(fontsize = 7)
    )
  }

@@

```{r phaseograms_whole_genome}
if(global_save_var){
  pdf(file = 'Manuscript_SuppFig5_phaseogram_allgenes.pdf',
      height = 5,
      width = 5)
  draw_heatmap_zscore(zscore_list = chab_z.list,
                      gene_ordering_vector = phaseogram_time_order$RMT$zscore_order$Geneid,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = FALSE)
  dev.off()
}

draw_heatmap_zscore(zscore_list = chab_z.list,
                    gene_ordering_vector = phaseogram_time_order$RMT$zscore_order$Geneid,
                    use_times = TRUE,
                    use_order_vector = FALSE,
                    show_row_names = FALSE,
                    tpm_mat = FALSE)

>>>>

library('readr')
library('dplyr')
library('ggplot2')
library("RColorBrewer")
library('data.table')
library('tibble')
library('stringr')
library('kableExtra')
library('viridis')
library('reshape2')
library('ComplexHeatmap')
library('circlize') # for circular plots and colour
library("factoextra")
library("MatrixGenerics") # for rowMins and rowMax

@@

names(phaseogram_row_order) <- c('rMT', 'SBP')

phaseogram_time_order <- lapply(names(phaseogram_row_order), 
                                function(list_element){
                                  transmission_list <- getElement(phaseogram_row_order,
                                                                  list_element)
                                  order_by_time <- transmission_list$zscore_order %>% 
                                    mutate(stage = str_extract(stage,
                                                               pattern = '[[:digit:]]{2}h')) %>% 
                                    arrange(stage)
                                  return(list(zscore_order = order_by_time))
                                }
)
names(phaseogram_time_order) <- names(phaseogram_row_order)

@@

    #Set the filter_genes_vector as the genes to remove if it doesn't already exist.
    if(is.null(filter_genes_vector)){
      filter_genes_vector <- remove_genes
    }else{
      filter_genes_vector <- filter_genes_vector[!filter_genes_vector %in% remove_genes]
    }

@@

                       if(tpm_mat){
                         #Get max/min TPM scores for the side annotation heatmap                       
                         tpm_mat.mat <- list_element$tpm[match(rownames(heatmap_data),
                                                           list_element$tpm$Geneid),] %>%
                           select(-Geneid) %>% 
                           as.matrix %>% 
                           log1p

                         tpm_min <- rowMins(tpm_mat.mat)
                         tpm_max <- rowMaxs(tpm_mat.mat)

@@

                         tpm_ha <- rowAnnotation(
                           min.max = anno_simple(cbind(tpm_min, 
                                                       tpm_max), 
                                                 col = tpm_col_fun,
                                                 # gp = gpar(col = 'black',
                                                 #           lwd = 0.1),
                                                 # border = TRUE,
                                                 simple_anno_size = unit(0.2, "cm")),
                           show_annotation_name = FALSE)
                       }

                       #Draw the left annotation only for the first element of the heatmap list.

@@

  if(tpm_mat){
    #Draw the legend
    tpm_lgd <- Legend(
      title = "Min/Max log(TPM + 1)", 
      col_fun = tpm_col_fun, 
      at = tpm_breaks, 
      labels = tpm_breaks,
      title_gp = gpar(fontsize = 7)
    )
  }

@@

```{r phaseograms_whole_genome}
if(global_save_var){
  pdf(file = 'Manuscript_SuppFig5_phaseogram_allgenes.pdf',
      height = 5,
      width = 5)
  draw_heatmap_zscore(zscore_list = chab_z.list,
                      gene_ordering_vector = phaseogram_time_order$rMT$zscore_order$Geneid,
                      use_times = TRUE,
                      use_order_vector = FALSE,
                      show_row_names = FALSE,
                      tpm_mat = FALSE)
  dev.off()
}

draw_heatmap_zscore(zscore_list = chab_z.list,
                    gene_ordering_vector = phaseogram_time_order$SBP$zscore_order$Geneid,
                    use_times = TRUE,
                    use_order_vector = FALSE,
                    show_row_names = FALSE,
                    tpm_mat = TRUE)
